Manuscript Figures

### 2021-09-14 src/manuscript_figures.Rmd
set global fig.width and fig.height to A4 dimensions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = params$workdir)
settings <- yaml::read_yaml(params$settings_file)
message(settings$GDCdataDir)
FigureFolder <- params$figures_folder
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ggridges)
library(ggcorrplot)
library(ComplexHeatmap)
library(pheatmap)
library(survminer)
library(survival)
library(caret)
library(treeheatr)
library(partykit)

@@

```{r pancancer_prediction, fig.height=9, fig.width=12}
# In this section, we make figures about pan-cancer classification 
# and some benchmarks of cohort-based unsupervised clustering across cancers

@@

```{r clinical_survival_factors, fig.width=12, fig.height=8}
# here we compute LFs associated to clinical factors (e.g. tumor stage, gender etc) and 
# survival outcomes (PFI)

@@

```{r msi_stats, fig.width=10, fig.height=8}
# Predicting MSI status using latent factors
# predict MSI status for pan-gastrointestinal tumors
# read MSI data
dataDir <- settings$GDCdataDir
MSI <- do.call(rbind, lapply(projectDict$`pan-gastrointestinal`, function(pr) {
  f <- file.path(dataDir, paste0(pr, '.MSI.tsv'))
  dt <- data.table::fread(f)[,c(2,4)]
  colnames(dt)[2] <- 'MSI'
  dt$project <- pr
  return(dt)
}))
# remove samples with undertermined MSI status
MSI <- MSI[MSI %in% c('MSI-H', 'MSI-L', 'MSS')]

@@

```{r print_figures, results='asis', include=TRUE, fig.width=10, fig.height=11}
base_url <- 'https://bimsbstatic.mdc-berlin.de'
for(i in 1:length(Figures)) {
  fig.url <- gsub("/data/bimsbstatic/public", base_url, file.path(FigureFolder, names(Figures)[i]))
  cat("# Figure",i,"[high-res image](",fig.url,")\n\n")
  print(Figures[[i]])
  cat("\n\n Figure",i,":",Legends[[i]],"\n\n")
}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8.27, fig.height = 11.69)
knitr::opts_knit$set(root.dir = params$workdir)
settings <- yaml::read_yaml(params$settings_file)
message(settings$GDCdataDir)
FigureFolder <- params$figures_folder
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ggridges)
library(ggcorrplot)
library(ComplexHeatmap)
library(pheatmap)
library(survminer)
library(survival)
library(caret)
library(treeheatr)
library(partykit)

@@

```{r pancancer_prediction}
# In this section, we make figures about pan-cancer classification 
# and some benchmarks of cohort-based unsupervised clustering across cancers

@@

```{r clinical_survival_factors}
# here we compute LFs associated to clinical factors (e.g. tumor stage, gender etc) and 
# survival outcomes (PFI)

@@

```{r tumor_purity}

```

```{r msi_stats}
# Predicting MSI status using latent factors
# predict MSI status for pan-gastrointestinal tumors
# read MSI data
dataDir <- settings$GDCdataDir
MSI <- do.call(rbind, lapply(projectDict$`pan-gastrointestinal`, function(pr) {
  f <- file.path(dataDir, paste0(pr, '.MSI.tsv'))
  dt <- data.table::fread(f)[,c(2,4)]
  colnames(dt)[2] <- 'MSI'
  dt$project <- pr
  return(dt)
}))
# remove samples with undertermined MSI status
MSI <- MSI[MSI %in% c('MSI-H', 'MSI-L', 'MSS')]

@@

```{r print_figures, results='asis', include=TRUE}
base_url <- 'https://bimsbstatic.mdc-berlin.de'
for(i in 1:length(Figures)) {
  fig.url <- gsub("/data/bimsbstatic/public", base_url, file.path(FigureFolder, names(Figures)[i]))
  cat("# Figure",i,"[high-res image](",fig.url,")\n\n")
  print(Figures[[i]])
  cat("\n\n Figure",i,":",Legends[[i]],"\n\n")
}
